### 2023-07-14 my_paper/Hadah-last-names.tex
edit pdf
create sum tab for mex and nonmex hispanics
edit

\linespread{1}{\title{{\fontfamily{ptm}
\selectfont{\Large{\MakeUppercase{The Impact of Hispanic Last Names and Identity on Labor Market Outcomes}}}}}}
	\author{{\fontfamily{pbk}\selectfont\large{\textsc{Hussain Hadah}}\thanks{Department of Economics, University of Houston, 206A McElhinney Hall, 3623 Cullen Boulevard, Houston, TX 77204-5019, United States (e-mail: \email{hhadah@uh.edu}).}}}
	\date{\fontfamily{pbk}\selectfont\normalsize{\textsc{\today}}}
	\maketitle

@@

\begin{abstract} 
In this paper, I study discrimination against Hispanics in the labor market. I compare the children of inter-ethnic marriages to study the impact of having a Hispanic last name. While males born to Hispanic father-White mothers earn 6 percentage points less than those born to White father-Hispanic mothers, the gap could be completely explained by educational differences. I also study the effect of identifying as Hispanic on earnings. I find that men with a Spanish-sounding last name who identify as Hispanic earn significantly less than those who do not identify as Hispanic, but the gap could also be explained by educational differences.
\end{abstract}

@@

$\beta_{1}$ is the coefficient of interest in this specification. $\beta_{1}$ estimates the earnings gaps between children of inter-ethnic marriages who have a Spanish-sounding last name versus a White last name.

@@

>>>>

\linespread{1}{\title{{\fontfamily{ptm}
\selectfont{\Large{\MakeUppercase{The Impact of Hispanic Last Names and Identity on Labor Market Outcomes}}}}}}
	\author{{\fontfamily{pbk}\selectfont\large{\textsc{Hussain Hadah}}\thanks{Department of Economics, Tulane University, 6823 St. Charles Ave., New Orleans, LA 70118, United States (e-mail: \email{hhadah@tulane.edu}).}}}
	\date{\fontfamily{pbk}\selectfont\normalsize{\textsc{\today}}}
	\maketitle

@@

\begin{abstract} 
In this paper, I study discrimination against Hispanics in the labor market. I compare the children of inter-ethnic marriages to study the impact of having a Hispanic last name. While males born to Hispanic father-White mothers earn 6 percentage points less than those born to White father-Hispanic mothers, the gap could be completely explained by educational differences. I also study the effect of identifying as Hispanic on earnings. I find that men with a Spanish-sounding last name who identify as Hispanic earn significantly less than those who do not identify as Hispanic, but the gap could also be explained by educational differences.

\keywords{Economics of Minorities, Race, and Immigrants; Discrimination and Prejudice.}
\JEL{J71; J64}

\end{abstract}

@@

$\beta_{1}$ is the coefficient of interest in this specification. $\beta_{1}$ represents the earnings gaps between children of inter-ethnic marriages who have a Spanish-sounding last name versus a White last name.

@@

\input{tables/tab03a-summary-stats-mex}

\input{tables/tab03a-summary-stats-nonmex}
